ropenblas: Download, Compile and Link OpenBLAS Library with R

### 2021-03-11 paper/paper.Rmd
Update

Table 1 below presents the benefit of considering an optimized version of BLAS. Computational costs are presented in the calculation of the singular decomposition in a rectangular matrix (`svd()`) and in the calculation of the inverse of that same matrix (`solve()` function). Some repetitions (100 repetitions) of each of the respective functions were performed. The benchmark can be better observed through the violin plots shown in Figure 2.

>>>>

Table 1 below presents the benefit of considering an optimized version of BLAS. Computational costs are presented in the calculation of the singular decomposition in a rectangular matrix (`svd()` function) and in the calculation of the inverse of that same matrix (`solve()` function). Some repetitions (100 repetitions) of each of the respective functions were performed. The benchmark can be better observed through the violin plots shown in Figure 2.
